### 2020-01-09 defesa/tex/chapter/e3p.tex
wip

It is possible to make another reduction to obtain a degree-$6$ polynomial, this can lower the size of the companion matrix utilized on obtaining the roots of $h$ from $12^2=144$ to $6^2=36$.
As it has been mentioned before, an ellipse is symmetric with respect to its own major or minor axis. 
In other words, rotating an ellipse by $\theta \in [0, \pi)$ is the same as rotating the same ellipse by $\pi + \theta$.
On the other hand, in \autoref{chapter:definitions}, it was stated that the angle of the complex numbers $z$ and $-z$ has the same symmetry with each other as the aforementioned symmetry of ellipses:
\begin{equation*}
angle(-z) = \pi + angle(z).
\end{equation*}
From that, as $g(e^{i\theta})=\xi(\theta)$ for every $\theta \in [0, 2\pi)$, we conclude that $g(-z)=g(z)$. This implies that $h$ is, in fact, an even polynomial, or that $h(-z) = h(z)$ is true for every $z\in\mathbb{C}$:
\begin{align}
h(-z) = (-z)^6g(-z) = z^6g(z).
\end{align}
Therefore, all the odd degree coefficients of $h$ are zero and we can define the $6$-degree polynomial $f : \mathbb{C} \mapsto \mathbb{C}$ with the substitution $y=z^2$ as follows
\begin{equation}
f(y) = \sum_{k=0}^{6} c_{2k} y^k.
\end{equation}
Then from every root $\hat{y}$ of $f$, two roots of $h$ can be obtained: $\sqrt{\hat{y}}$ and $-\sqrt{\hat{y}}$. As the angle of one of the roots will not be between $[0, \pi)$ we can ignore one of them. 
Note that the the square root of $\hat{y}$ does not need to be calculated, as only the angles are needed and they can be obtained by the following identity
\begin{equation}
angle(\sqrt{z}) = angle(z)/2.
\end{equation}
Finally, using the QR algorithm mentioned in \autoref{chapter:definitions}, a $\bigO(n^3)$ algorithm can be constructed for E3PNT. Because $n$ will always be $6$, we can say that we have a $\bigO(1)$ algorithm that takes around $6^3$ operations.

It is also worth mentioning that a pattern on the coefficients of $f$ was identified, and maybe, for future work, it can be used for further improvements. Analyzing the polynomials produced for several instances, the following seems to be true:
\begin{equation}\label{eq:palindromic_pol}
c_k = \overline{c_{6-k}},
\end{equation}
for $k=0, \dots, 6$. For now, we neither have any ideas on how \autoref{eq:palindromic_pol} could be proved nor how it could be used for further improving our algorithm.

Assuming that an algorithm to obtain the eigenvalues of a matrix, the following algorithm to obtain every solution of E3PNT is described in \autoref{algoritmo:e3p}.

\section{Numerical Experiments}

@@

		\For{$i\in\{1, \dots, 6\}$}\Comment{Constructing the companion matrix.}
			\State $A_{i,i+1} \gets 1$
			\State $A_{6,i} \gets -\dfrac{c_{i-1}}{c_6}$
		\EndFor

@@

		\ForAll{$q \in eig(A)$} \Comment{$eig(A)$ returns every eigenvalue of $A$.}
		\State $\theta\gets angle(q)$
		\If{$|\theta|=1$}
			\State $Q \gets Q \cup \{\theta\}$
		\EndIf
		\EndFor

		\State $Sols\gets\{\}$
		\ForAll{$\theta\in Q$}
		\State Let $c$ be the center of the circumscribe circle of $\Lambda(\theta)$.
		\State $Sols \gets \cup \{(\varphi^{-1}(c, \theta)+u, \theta)\}$
		\EndFor

		\State \Return $Sols$
		\EndProcedure
	\end{algorithmic}
\end{algoritmo}

>>>>

It is possible to make another reduction to obtain a degree-$6$ polynomial.
As it has been mentioned before, an ellipse is symmetric with respect to its own major or minor axis. 
In other words, rotating an ellipse by $\theta \in [0, \pi)$ is the same as rotating the same ellipse by $\pi + \theta$.
On the other hand, in \autoref{chapter:definitions}, it was stated that the angle of the complex numbers $z$ and $-z$ has the same symmetry with each other as the aforementioned symmetry of ellipses:
\begin{equation*}
angle(-z) = \pi + angle(z).
\end{equation*}
From that, as $g(e^{i\theta})=\xi(\theta)$ for every $\theta \in [0, 2\pi)$, we conclude that $g(-z)=g(z)$. This implies that $h$ is, in fact, an even polynomial, or that $h(-z) = h(z)$ is true for every $z\in\mathbb{C}$:
\begin{align}
h(-z) = (-z)^6g(-z) = z^6g(z).
\end{align}
Therefore, all the odd degree coefficients of $h$ are zero and we can define the $6$-degree polynomial $f : \mathbb{C} \mapsto \mathbb{C}$ with the substitution $y=z^2$ as follows
\begin{equation}
f(y) = \sum_{k=0}^{6} c_{2k} y^k.
\end{equation}
Then from every root $\hat{y}$ of $f$, two roots of $h$ can be obtained: $\sqrt{\hat{y}}$ and $-\sqrt{\hat{y}}$. As the angle of one of the roots will not be between $[0, \pi)$ we can ignore one of them. 
Note that the the square root of $\hat{y}$ does not need to be calculated, as only the angles are needed and they can be obtained by the identity
\begin{equation}
angle(\sqrt{z}) = angle(z)/2.
\end{equation}

It is also worth mentioning that a pattern on the coefficients of $f$ was identified, and maybe, for future work, it can be used for further improvements. Analyzing the polynomials produced for several instances, the following seems to be true:
\begin{equation}\label{eq:palindromic_pol}
c_k = \overline{c_{6-k}},
\end{equation}
for $k=0, \dots, 6$. For now, we neither have any ideas on how \autoref{eq:palindromic_pol} could be proved nor how it could be used to find the roots of $f$.

Finally, in the next section we use this approach of converting $\xi$ into a complex polynomial to develop an algorithm for E3PNT.

\section{An algorithm for E3PNT}

Among the approaches that have been described here, converting $\xi$ into a complex polynomial was the chosen one as the basis of the algorithm for E3PNT.
The other approach that showed good results was the numerical approximation one that uses Chebyshev interpolation. Ultimately this approach requires finding the eigenvalues of a companion matrix, this matrix, however, is usually going to be larger than the $6\times 6$, which is the size of the matrix needed to find the roots of the complex polynomial in \autoref{algoritmo:e3p}.

Details about getting the eigenvalues of a companion matrix, or determining the center of a circumscribed circle of a triangle are omitted from \autoref{algoritmo:e3p} for the sake of clarity and can be found elsewhere in this work. Also, we assume that the $angle$ function used in the algorithm returns the angle of a complex number in the interval $[0, 2\pi)$.

@@

		\For{$i\in\{1, \dots, 6\}$}\Comment{Constructing the companion matrix.}
			\State $A_{i,i+1} \gets 1$
			\State $A_{6,i} \gets -\dfrac{c_{2(i-1)}}{c_{12}}$
		\EndFor

@@

		\ForAll{$q \in eig(A)$} \Comment{$eig(A)$ returns every eigenvalue of $A$.}
		\State $\theta\gets \min\{angle(-q)/2, angle(q)/2\}$
		\If{$|\theta|=1$}
			\State Let $c$ be the center of the circumscribe circle of $\Lambda(\theta)$.
			\State $Q \gets Q\cup \{(\varphi^{-1}(c, \theta)+u, \theta)\}$
		\EndIf
		\EndFor

		\State \Return $Q$
		\EndProcedure
	\end{algorithmic}
\end{algoritmo}

\begin{teorema}
	The \autoref{algoritmo:e3p} computes every solution of E3PNT in $\bigO(1)$ operations.
\end{teorema}

\begin{proof}
	It has already been shown that computing every root of $\xi$ through the complex polynomial yields every solution of E3PNT, the only thing left to prove is the running time of the algorithm.
	Computing every eigenvalue of a matrix can be done in $\bigO(n^3)$, but as for our case $n$ is fixed at $6$, it can be stated that computing the eigenvalues for the companion matrix of $f$ can be done in $\bigO(1)$. Therefore, the whole algorithm runs in constant time.
\end{proof}

In this section we show the results of an experiment made to study the numerical stability of \autoref{algoritmo:e3p}.
For every root found $\hat{\theta}$, we measure its error by $|\xi(\hat{\theta})$|.

We generate random instances according to a normal distribution with $0$ mean and standard deviation $K$. We tried different values for $K$ and generated $1000$ instances for each one. The maximum error and the average error for different values of $K$ can be seen in \autoref{fig:e3p_error}.

From this experiment we can say that \autoref{algoritmo:e3p} has a good numerical stability as the accuracy of the roots found shows to have a linear relation .
